Coupling finite and boundary element methods to solve the Poisson-Boltzmann equation for electrostatics in molecular solvation

### 2022-10-13 main.tex
Cleaning references
I put accessed November 4, 2020, but I do not know when did we take Arginine data.

\clearpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% FIGURE CAPTIONS

%%%%% FIGURE ---- cc.eps
\begin{figure}
\caption{\label{cc} Place Figure 1 caption here. In the case of reproduced figures in review articles, you must obtain the publisher's permission and state a suitable notice here along with a citation.}
\end{figure}

\begin{figure}
\caption{\label{fig2} Place Figure 2 caption here. Figures should be uploaded as individual files, preferably .tif or .eps files, at high enough resolution (600 to 1200 dpi) to ensure clarity. Please see the author’s guide for more details and specifications. For high quality illustrations, we highly recommend the use of the TikZ package.}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% FIGURE FILES

%\vspace*{0.1in}   %%% FIGURE 1
%\begin{center}
%\includegraphics[width=0.2\columnwidth,keepaspectratio=true]{cc.eps}
%\end{center}
\vspace{0.25in}
\hspace*{3in}
{\Large
\begin{minipage}[t]{3in}
\baselineskip = .5\baselineskip
Figure 1 \\
Author A, Author B, Author C, Author D \\
J.\ Comput.\ Chem.
\end{minipage}
}

\begin{table}
\begin{tabular}{|c|c|c|c|}\hline
\textbf{Quantity} & \textbf{Calculated} & \textbf{Observed} & \textbf{Error} \\ \hline
  Density & 5.3 & 6.3 & Within limits \\ \hline
  Optical magnification & 8.3 & 90.9 & Utterly unacceptable\! \\ \hline
\end{tabular}
\caption{\label{tbl1} Place table caption here.}
\end{table}

>>>>

%\clearpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% FIGURE CAPTIONS
%
%%%%%% FIGURE ---- cc.eps
%\begin{figure}
%\caption{\label{cc} Place Figure 1 caption here. In the case of reproduced figures in review articles, you must obtain the publisher's permission and state a suitable notice here along with a citation.}
%\end{figure}
%
%\begin{figure}
%\caption{\label{fig2} Place Figure 2 caption here. Figures should be uploaded as individual files, preferably .tif or .eps files, at high enough resolution (600 to 1200 dpi) to ensure clarity. Please see the author’s guide for more details and specifications. For high quality illustrations, we highly recommend the use of the TikZ package.}
%\end{figure}
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% FIGURE FILES
%
%\clearpage
%
%%\vspace*{0.1in}   %%% FIGURE 1
%%\begin{center}
%%\includegraphics[width=0.2\columnwidth,keepaspectratio=true]{cc.eps}
%%\end{center}
%\vspace{0.25in}
%\hspace*{3in}
%{\Large
%\begin{minipage}[t]{3in}
%\baselineskip = .5\baselineskip
%Figure 1 \\
%Author A, Author B, Author C, Author D \\
%J.\ Comput.\ Chem.
%\end{minipage}
%}
%
%\clearpage
%
%\begin{table}
%\begin{tabular}{|c|c|c|c|}\hline
%\textbf{Quantity} & \textbf{Calculated} & \textbf{Observed} & \textbf{Error} \\ \hline
%  Density & 5.3 & 6.3 & Within limits \\ \hline
%  Optical magnification & 8.3 & 90.9 & Utterly unacceptable\! \\ \hline
%\end{tabular}
%\caption{\label{tbl1} Place table caption here.}
%\end{table}
